The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-09-28 paper2_JNLS/paper.tex
NM

@@

@@

>>>>

% Definitely cite several of Sapsis's new papers.

@@

\subsection{Statistical comparison between theory and experiments}

@@

\subsection{Wave dynamics}

We show individual trajectories in the next figure for upstream and downstream. In the upstream flow, due to the coefficients, the nonlinearity is very weak. Hence, wave propagation is dominated by linear dispersion. Indeed, with weak nonlinearity, \eqref{dimlessKdV} is approximated by
\begin{equation}
u_t + C_2 \drat^{1/2} \, u_{xxx} = 0
\qquad \text{for } x \in [-\pi,\pi] \\
\end{equation}
which implies the dispersion relation $\omega_k = -C_2 k^3$ or for phase velocity $c_k = -C_2 k^2$, which implies left-going waves \cite{majdaqi2019}.
